---
title: "HWFWM Character Analysis - R Solutions"
author: "Data Science Team"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(corrplot)
library(scales)
library(gridExtra)
library(plotly)
library(cluster)
library(factoextra)
```

## Data Loading and Preparation

```{r load_data}
# Load the dataset
df <- read.csv("../data/processed_data.csv")

# Convert categorical variables to factors
df$Race <- as.factor(df$Race)
df$Class <- as.factor(df$Class)
df$Rank <- factor(df$Rank, levels = c("Iron", "Bronze", "Silver", "Gold", "Diamond", "Platinum"))
df$Evolution_Stage <- factor(df$Evolution_Stage, 
                           levels = c("Initiate", "Awakened", "Core", "Essence", "Transcendent"))
```

## Exploratory Data Analysis

### 1. Character Race Distribution

```{r race_distribution}
ggplot(df, aes(x = Race, fill = Race)) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Character Race Distribution",
       x = "Race",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### 2. Level Distribution Analysis

```{r level_distribution}
ggplot(df, aes(x = Level)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", color = "black") +
  geom_density(color = "red") +
  theme_minimal() +
  labs(title = "Character Level Distribution",
       x = "Level",
       y = "Density")
```

### 3. Core Stats Correlation Matrix

```{r core_stats_correlation}
core_stats <- df %>% 
  select(Power, Vitality, Spirit, Endurance, Magic)

cor_matrix <- cor(core_stats)
corrplot(cor_matrix, method = "color", type = "upper",
         addCoef.col = "black", tl.col = "black",
         title = "Core Stats Correlation Matrix")
```

### 4. Skill Rarity Distribution

```{r skill_distribution}
skill_cols <- c("Common_Skills", "Uncommon_Skills", "Rare_Skills", "Epic_Skills", "Legendary_Skills")
skill_data <- df %>%
  select(all_of(skill_cols)) %>%
  gather(key = "Rarity", value = "Count")

ggplot(skill_data, aes(x = Rarity, y = Count, fill = Rarity)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Skill Distribution by Rarity",
       x = "Skill Rarity",
       y = "Number of Skills") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Statistical Analysis

### 11. Power Level Statistical Tests

```{r power_analysis}
# Perform ANOVA
power_aov <- aov(Power ~ Race, data = df)
power_summary <- summary(power_aov)

# Create visualization
ggplot(df, aes(x = Race, y = Power, fill = Race)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Power Distribution by Race",
       subtitle = paste("ANOVA p-value:", format.pval(power_summary[[1]]$`Pr(>F)`[1])),
       x = "Race",
       y = "Power") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### 12. Survival Rate Analysis

```{r survival_analysis}
# Fit linear model
survival_model <- lm(Survival_Rate ~ Vitality + Endurance + Level, data = df)
model_summary <- summary(survival_model)

# Create coefficient plot
coef_data <- data.frame(
  Feature = names(coef(survival_model))[-1],
  Coefficient = coef(survival_model)[-1],
  SE = sqrt(diag(vcov(survival_model)))[-1]
)

ggplot(coef_data, aes(x = Feature, y = Coefficient)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_errorbar(aes(ymin = Coefficient - 1.96*SE, 
                    ymax = Coefficient + 1.96*SE),
                width = 0.2) +
  theme_minimal() +
  labs(title = "Survival Rate Factors",
       subtitle = paste("R-squared:", round(model_summary$r.squared, 3)),
       x = "Feature",
       y = "Coefficient Estimate") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Character Optimization

### 16. Optimal Stat Distribution

```{r optimal_stats}
# Calculate combat effectiveness score
df$Combat_Score <- with(df, (Damage_Output * 0.4 + 
                            Survival_Rate * 0.4 + 
                            Kill_Count * 0.2))

# Get top performers
top_performers <- df %>%
  arrange(desc(Combat_Score)) %>%
  head(50)

# Create parallel coordinates plot using plotly
plot_ly(
  type = 'parcoords',
  line = list(color = top_performers$Combat_Score,
              colorscale = 'Viridis'),
  dimensions = list(
    list(range = c(min(top_performers$Power), max(top_performers$Power)),
         label = 'Power', values = top_performers$Power),
    list(range = c(min(top_performers$Vitality), max(top_performers$Vitality)),
         label = 'Vitality', values = top_performers$Vitality),
    list(range = c(min(top_performers$Spirit), max(top_performers$Spirit)),
         label = 'Spirit', values = top_performers$Spirit),
    list(range = c(min(top_performers$Endurance), max(top_performers$Endurance)),
         label = 'Endurance', values = top_performers$Endurance),
    list(range = c(min(top_performers$Magic), max(top_performers$Magic)),
         label = 'Magic', values = top_performers$Magic)
  )
)
```

## Progression Analysis

### 21. Level Progression Patterns

```{r level_progression}
ggplot(df, aes(x = Rank, y = Level, fill = Rank)) +
  geom_violin() +
  geom_boxplot(width = 0.1, fill = "white") +
  theme_minimal() +
  labs(title = "Level Distribution by Rank",
       x = "Rank",
       y = "Level") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### 22. Skill Acquisition Rate

```{r skill_acquisition}
ggplot(df, aes(x = Level, y = Total_Skills)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", formula = y ~ x) +
  theme_minimal() +
  labs(title = "Skill Acquisition Rate",
       x = "Level",
       y = "Total Skills")
```

## Combat Effectiveness

### 26. Damage Output Factors

```{r damage_factors}
# Fit random forest model
library(randomForest)
features <- c("Power", "Vitality", "Spirit", "Endurance", "Magic", "Level")
rf_model <- randomForest(Damage_Output ~ ., 
                        data = df[, c(features, "Damage_Output")],
                        importance = TRUE)

# Create importance plot
importance_data <- data.frame(
  Feature = features,
  Importance = importance(rf_model)[,1]
) %>%
  arrange(desc(Importance))

ggplot(importance_data, aes(x = reorder(Feature, Importance), y = Importance)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme_minimal() +
  labs(title = "Damage Output - Feature Importance",
       x = "Feature",
       y = "Importance") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### 30. Elite Character Analysis

```{r elite_analysis}
# Calculate performance score
df$Performance_Score <- with(df, 
  rank(Damage_Output)/length(Damage_Output) * 0.4 +
  rank(Survival_Rate)/length(Survival_Rate) * 0.4 +
  rank(Kill_Count)/length(Kill_Count) * 0.2
)

# Get top 5% performers
elite_chars <- df %>%
  arrange(desc(Performance_Score)) %>%
  head(round(nrow(df) * 0.05))

# Create multiple plots
p1 <- ggplot(elite_chars, aes(y = Power)) +
  geom_boxplot(fill = "skyblue") +
  theme_minimal() +
  labs(title = "Power Distribution",
       y = "Power")

p2 <- ggplot(elite_chars, aes(x = Class, fill = Class)) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Class Distribution",
       x = "Class") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p3 <- ggplot(elite_chars, aes(x = Race, fill = Race)) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Race Distribution",
       x = "Race") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(p1, p2, p3, ncol = 2)
```

## Session Info

```{r session_info}
sessionInfo()